Something something values disclosure replication

### 2022-07-05 paper/paper.Qmd
switch paper paths to here()

---
title: "Something something values disclosure replication"
author: "Daniel J. Hicks and Emilio Lobato"
abstract: |
  abstract
---

@@

![Participant values by political ideology. (A) Absolute counts, (B) shares within political ideology categories.  Panel (A) shows that our sample substantially over-represents political liberals.](../out/03_part_values.png){#fig-part-values}

@@

```{r}
#| echo: false
#| label: tbl-bc
#| tbl-cap: "Regression analysis for hypotheses H2 (consumer risk sensitivity) and H3 (disclosure effect)"
bc_tbl = readRDS('../out/03_bc_tbl.Rds')
bc_tbl
```

@@

![Directed acyclic graph (DAG) for analysis of the shared values effect.  If the DAG is faithful, adjusting for scientist values (`sci_values`) and participant values (`part_values`) is sufficient for estimating the effect of shared values on perceived trustworthiness (`METI`).  In particular, adjusting for demographics should not change the regression coefficient on shared values.](../out/03_shared_values_dag.png){#fig-shared-dag}

```{r}
#| echo: false
#| label: tbl-shared
#| tbl-cap: "Sequential regression analysis of hypothesis H4 shared values/scientist values effects"
shared_values_tbl = readRDS('../out/03_shared_values_tbl.Rds')
shared_values_tbl
```

@@

```{r}
#| echo: false
#| label: tbl-eb
#| tbl-cap: "Regression analysis of H5b, interaction between participant values and consumer risk sensitivity"
readRDS('../out/03_eb_tbl.Rds')
```

@@

```{r}
#| echo: false
#| label: tbl-ec
#| tbl-cap: "Regression analysis of H5c, interaction between participant values and disclosure effect"
readRDS('../out/03_ec_tbl.Rds')
```

@@

![Data, group means, and 95% confidence intervals for H5d, interaction of shared values and participant values.  Panels correspond to participant values.](../out/03_shared_part.png){#fig-shared-part}

@@

![Data, group means, and 95% confidence intervals for a potential interaction of scientist values and participant values. Panels correspond to participant values. This figure is identical to @fig-shared-part, except the columns in the economic growth panel have been switched.](../out/03_sci_part.png){#fig-sci-part}

```{r}
#| echo: false
#| label: tbl-sci-part
#| caption: "Regression analysis of interaction between scientist values and participant values"
readRDS('../out/03_sci_part_tbl.Rds')
```

>>>>

---
title: "Something something values disclosure replication"
author: "Daniel J. Hicks and Emilio Lobato"
abstract: |
  abstract
execute:
    echo: false
---

```{r}
#| message: false
#| results: hide

library(here)
here()
out_dir = here('out')
```

@@

![Participant values by political ideology. (A) Absolute counts, (B) shares within political ideology categories.  Panel (A) shows that our sample substantially over-represents political liberals.](`r here(out_dir, '03_part_values.png')`){#fig-part-values}

@@

```{r}
#| label: tbl-bc
#| tbl-cap: "Regression analysis for hypotheses H2 (consumer risk sensitivity) and H3 (disclosure effect)"
bc_tbl = readRDS(here(out_dir, '03_bc_tbl.Rds'))
bc_tbl
```

@@

![Directed acyclic graph (DAG) for analysis of the shared values effect.  If the DAG is faithful, adjusting for scientist values (`sci_values`) and participant values (`part_values`) is sufficient for estimating the effect of shared values on perceived trustworthiness (`METI`).  In particular, adjusting for demographics should not change the regression coefficient on shared values.](`r here(out_dir, '03_shared_values_dag.png')`){#fig-shared-dag}

```{r}
#| label: tbl-shared
#| tbl-cap: "Sequential regression analysis of hypothesis H4 shared values/scientist values effects"
shared_values_tbl = readRDS(here(out_dir, '03_shared_values_tbl.Rds'))
shared_values_tbl
```

@@

```{r}
#| label: tbl-eb
#| tbl-cap: "Regression analysis of H5b, interaction between participant values and consumer risk sensitivity"
readRDS(here(out_dir, '03_eb_tbl.Rds'))
```

@@

```{r}
#| label: tbl-ec
#| tbl-cap: "Regression analysis of H5c, interaction between participant values and disclosure effect"
readRDS(here(out_dir, '03_ec_tbl.Rds'))
```

@@

![Data, group means, and 95% confidence intervals for H5d, interaction of shared values and participant values.  Panels correspond to participant values.](`r here(out_dir, '03_shared_part.png')`){#fig-shared-part}

@@

![Data, group means, and 95% confidence intervals for a potential interaction of scientist values and participant values. Panels correspond to participant values. This figure is identical to @fig-shared-part, except the columns in the economic growth panel have been switched.](`r here(out_dir, '03_sci_part.png')`){#fig-sci-part}

```{r}
#| label: tbl-sci-part
#| tbl-cap: "Regression analysis of interaction between scientist values and participant values"
readRDS(here(out_dir, '03_sci_part_tbl.Rds'))
```
